Effects of the body force on the evacuation dynamics

### 2019-12-31 paper.tex
agregue un pedazo de texto a network bottleneck

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn0.eps}\label{flow_density_nocomp}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn0.eps}\label{flow_density_comp}}\\
        \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn1200000.eps}\label{flow_density_nocomp}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn1200000.eps}\label{flow_density_comp}}\\
\caption[width=0.47\columnwidth]{}
\label{flow_density}
\end{figure}

@@

\section{appendix_1}

@@

\begin{equation}
 \displaystyle\frac{d\mathbf{v}'}{dt'}=
 \hat{\mathbf{e}}_d-\mathbd{v}'+\mathcal{A}\,e^{R'-r'}\,
 \hat{\mathbf{n}}+g(R'-r')\,\bigg[\mathcal{K}\,(\Delta\mathbf{v}'\cdot
 \hat{\mathbf{t}})\,\hat{\mathbf{t}}+\mathbf{K}_c\,\hat{\mathbf{n}}\bigg]
\end{equation}

>>>>

Increasing the stiffness has a significative impact on the evacuation dynamics. It reduces the overlap and reduces the mean degree between pedestrians. Both effects tend to reduce the friction in the crowd and the immediate consequence of this is a reduction of the evacuation time (pedestrians escape faster). The body force has a notorious impact in the number of pedestrians that each pedestrians touch (degree). This is clearly depicted in Fig. \ref{network_bottleneck} where four different configurations of the evacuation dynamics are shown. The configurations represent 225 pedestrians trying to escape through a 0.92 m door which center is located at $(x,y)=(20,10)$~m. The colors correspond to the degree of each node (pedestrian) and the lines between pedestrians represent the contacts among them.\\

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn0.eps}\label{network_vd2_kn0}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn0.eps}\label{network_vd10_kn0}}\\
        \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn1200000.eps}\label{network_vd2_kn1200000}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn1200000.eps}\label{network_vd10_kn1200000}}\\
\caption[width=0.47\columnwidth]{}
\label{network_bottleneck}
\end{figure}

@@

%\section{appendix_1}

@@

%\begin{equation}
% \displaystyle\frac{d\mathbf{v}'}{dt'}=
% \hat{\mathbf{e}}_d-\mathbd{v}'+\mathcal{A}\,e^{R'-r'}\,
% \hat{\mathbf{n}}+g(R'-r')\,\bigg[\mathcal{K}\,(\Delta\mathbf{v}'\cdot
% \hat{\mathbf{t}})\,\hat{\mathbf{t}}+\mathbf{K}_c\,\hat{\mathbf{n}}\bigg]
%\end{equation}
